Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-15 publication_materials/ms_rbc.tex
rev2a

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important trends remain elusive -- particularly in the large Rayleigh number regime.
In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. 
We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
\end{abstract}

@@

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and fueling small-scale processes in important systems \cite{Couston}.

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
State of the art convection simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.

Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of ECS. Should that be the case, it is crucial that we discover and classify such states.

@@

\section{Model Setup}\label{sec:model}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
The equations of motion are then given by
\begin{align}
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
\end{align}
where $p$ is pressure and $T$ is temperature. 
For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, boundary temperature difference, kinematic viscosity, and thermal diffusivity respectively. For convenience, we define
\begin{equation}
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
\end{equation}

To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
\begin{align}
    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z, t) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z, t) + A(t) p'(x, z, t) \label{EQ:reynolds_dc_p}.
\end{align}
where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. Perturbations must admit no horizontal-average; an arbitrary perturbation $f'$ obeys
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
\begin{equation}
  \langle T'^2 \rangle_{\mathcal{D}} = 1
\end{equation}
thereby alleviating any ambiguity in $A(t)$. 
Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
\begin{equation}
  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$. It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$. However we must have $\bar{w}(z, t) = 0$ due to incompressibility.

@@

At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
We also assume this term is composed of eigenfunctions belonging to the dominant mode(s).

\section{Perturbation Evolution}
Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A(t)$. 
To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
Stable modes decay away rapidly. 
Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to tends to stabilize $\bar{T}$, thereby creating a negative feedback loop. Only marginally stable modes can traverse this hypothetical time-scale separation. Therefore the amplitude function $A(t)$ must satisfy
\begin{equation}
    \max_{k_x} \{ \omega \} = 0.
\end{equation}

For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE) $\bar{T}_{\rm{MSTE}}$, thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.

At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
This generally involves a unique and unknown value $A^2(t_0) > 0$. 
Our method of finding $A^2(t_0)$ is best illustrated through example.

@@

An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}(z, t_0)$ tends to increase its eigenvalues. 
Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2(t_0)$ can then be approximated by
\begin{equation}
    A^2(t_0) \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
\end{equation}
where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode (corresponding to the light blue and green points respectively at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}). 
$\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion $|\omega_{\rm{max}} (A^2)| \leq 10^{-9}$. 
The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another. 
In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.

@@

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are solutions to the quasilinear form of the Rayleigh-B\'enard convection equations derived in section \ref{sec:model}. 
For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
Their mean temperatures $\bar{T}_{\rm{MSTE}}$ are symmetric about $z = 0$ by construction.

@@

The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. 
These dips appear in every solution, regardless of $Ra$. 
Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}.  
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{Mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
    The initial profile is given by (\ref{EQ:T0}). 
    The MSTE curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
    The DNS profile is obtained by performing a 2-dimensional nonlinear simulation of (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus} until thermal and kinetic relaxation. 
    The DNS temperature data are horizontally- and time-averaged. 
    The initial, MSTE, and DNS profiles have increasingly relaxed boundary regions (respectively). 
    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midplanes of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.}
    \label{fig:T0_profiles}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$). 
    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\end{figure}
\begin{figure*}
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). 
    Advection profiles belong to marginally-stable modes. 
    For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
    For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
    A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for MSTE, aspect-ratio optimized ECS \cite{Wen}, and statistically-steady DNS \cite{Johnston, Scheel_2016}.
    All datasets obey power-law relationships, with MSTE admitting classical scaling $\Nu \sim Ra^{1/3}$. 
    MSTE facilitate more heat transfer than the ECS and DNS, as can be explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$. 
    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
    We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse. 
    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers. 
    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
    \label{fig:del_inv}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus_1954}}
    \label{fig:bl_ra}
\end{figure}

Equilibrated states exhibit distinct behaviors for large and small $Ra$. 
This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. 
For lower $Ra$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
These states have relaxed boundary layers which gradually subside as advection becomes the dominant component of the total flux. 
Such transitional regions do not appear in high $Ra$ cases, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes adjacent to the third presumed local maximum in the eigenvalue spectrum. 
Traversing towards the midplane of the domain, we see increasingly thicker advection profiles corresponding the wavenumbers adjacent to the second local maximum, eventually culminating in the dominant $k_x = 1.5\pi$ mode.

>>>>

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. 
We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
\end{abstract}

@@

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating large-scale behaviors and generating small-scale processes in important systems \cite{Couston}.

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
State of the art simulations performed by \cite{Zhu_2018} have reached $Ra \sim 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu \sim Ra^{\beta}$ in the asymptotic ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus_1954, Howard_1966, Kraichnan, Spiegel, Castaing, Grossman, Ahlers}.

Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
Much of the published work on this topic relates to unstable exact coherent states (ECS) \cite{Waleffe, Sondak, Wen, chini_cells}. 
Simulations and analysis performed by \cite{Yalniz, Cvitanovic} suggest that chaotic simulation trajectories can be represented by a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable equilibria. Should that be the case, it is crucial that we discover and classify such equilibria.

@@

\section{Model Setup}\label{sec:model}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
The domain $\mathcal{D}$ is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
The fluid of interest is constrained between two flat boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
The equations of motion are then given by
\begin{align}
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \mathcal{R} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \mathcal{P} \nabla^2 T \label{EQ:motion3}
\end{align}
where $p$ is pressure and $T$ is temperature. 
For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
Any system of this form can be characterized by its dimensionless Rayleigh number $Ra = \frac{g\alpha L^3 \Delta T}{\nu \kappa}$ and Prandtl number $Pr = \frac{\nu}{\kappa}$, where $g, \, \alpha, \, L, \, \Delta T, \nu, \kappa$ are the gravitational acceleration, coefficient of thermal expansion, domain height, opposed temperature difference, kinematic viscosity, and thermal diffusivity respectively. For convenience, we define
\begin{equation}
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
\end{equation}

To derive the quasilinear form, we posit that an arbitrary field $f$ can be represented as the sum of a mean profile (denoted by $\bar{f}$) and a perturbation function (denoted by $f'$).
\begin{align}
    \mathbf{u}(x, z, t) &= A(t) \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= A(t) u'(x, z, t)\hat{x} + A(t) w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z, t) + A(t) T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z, t) + A(t) p'(x, z, t) \label{EQ:reynolds_dc_p}.
\end{align}
where $A(t)$ is some unknown real amplitude and the mean-velocity components vanish due to incompressibility and symmetry. Perturbations must admit no horizontal-average
\begin{equation}
    \langle f'(x, z, t) \rangle_x \equiv \int_{0}^4 f'(x, z, t) dx = 0.
\end{equation}
Assuming the existance of nontrivial solutions, we also fix the volume-average over the entire domain
\begin{equation}
  \langle T'^2 \rangle_{\mathcal{D}} = 1
\end{equation}
thereby alleviating any ambiguity in $A(t)$. 
Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) and taking the horizontal average reduces the system to a simple initial value problem (IVP) for $\bar{T}$
\begin{equation}
  \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle_x = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
with associated boundary conditions $\bar{T}(-1/2, t) = 1$ and $\bar{T}(1/2, t) = 0$. It should be noted that we could obtain a similar IVP for $u$ by breaking symmetry and considering some nontrivial mean horizontal flow $\bar{u}(z, t)$. However we must have $\bar{w}(z, t) = 0$ due to incompressibility.

@@

At some arbitrary time $t_0$, the forcing term $\langle w'T' \rangle_x$ can be found by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$.

\section{Perturbation Evolution}
Solving the linearized system (\ref{EQ:linear1}) -- (\ref{EQ:linear3}) does not yield $A(t)$. 
To evolve $\bar{T}$, we assume the perturbations and mean quantities evolve according to different time-scales, as in \cite{michel_chini_2019}.
Stable modes decay away rapidly. 
Unstable modes will not persist on the slow time-scale because the advective term $\langle w'T' \rangle_x$ tends to stabilize $\bar{T}$, thereby creating a negative feedback loop. Only marginally stable modes can traverse this hypothetical time-scale separation. Therefore the amplitude function $A(t)$ must satisfy
\begin{equation}
    \max_{k_x} \{ \omega \} = 0.
\end{equation}

For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.

At $t = 0$, we begin with a marginally-stable initial profile $\bar{T}(z, 0)$ whose construction is outlined in \ref{sec:initial_profile}. 
At some arbitrary time $t = t_0$, we seek to evolve $\bar{T}(z, t_0)$ into a new marginally-stable profile $\bar{T}(z, t_0 + \Delta t)$ according to (\ref{EQ:T0_IVP}) via forward-Euler. 
This generally involves a unique and unknown value $A^2(t_0) > 0$. 
Our method of finding $A^2(t_0)$ is best illustrated through example.

@@

An iteration is performed as follows: diffusing a marginally-stable temperature profile $\bar{T}(z, t_0)$ tends to increase its eigenvalues. 
Ignoring the diffusive term and evolving according to advection tends the stabilize the system. The appropriate amplitude $A^2(t_0)$ can then be approximated by
\begin{equation}
    A^2(t_0) \sim -\frac{\omega_{\rm{diff}}}{\omega_{\rm{adv}}}
\end{equation}
where $\omega_{\rm{diff}}$ and $\omega_{\rm{adv}}$ refer to the diffused and advected eigenvalues of the initially marginal mode. These quantities correspond to the light blue and green points at $k_x = \pi$ in Figure \ref{fig:iteration_spectra}). 
$\bar{T}(z, t)$ is then evolved according to (\ref{EQ:T0_IVP}) and another eigenvalue solve is performed. 
Given a fixed timestep $\Delta t$, we assume the dominant eigenvalue can be described by a continuous function $\omega_{\rm{max}} (A^2)$ which is locally differentiable. 
We use Newton's method to find an amplitude which satisfies our marginal stability tolerance criterion. 
The dominant mode is not fixed; an iteration can facilitate the transfer of marginal-stability from one mode to another. 
In section \ref{sec:multiple_modes} we specify procedures for the treatment of multiple simultaneously marginal modes.

@@

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are solutions to the quasilinear form of the Rayleigh-B\'enard convection equations derived in section \ref{sec:model}. 
For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
Their mean temperatures $\bar{T}$ are symmetric about $z = 0$ by construction.

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{Mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
    The initial profile is given by (\ref{EQ:T0}). 
    The MSTE curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
    The DNS profile is obtained by performing a 2-dimensional nonlinear simulation of (\ref{EQ:motion1})--(\ref{EQ:motion3}) with \texttt{Dedalus} until thermal and kinetic relaxation. 
    The DNS temperature data are horizontally- and time-averaged. 
    The initial, MSTE, and DNS profiles have increasingly relaxed boundary regions (respectively). 
    The MSTE profile exhibits prominent dips, nested alongside the boundary regions. 
    The source of this feature is not well understood, but similar temperature gradient reversal regions were found by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.}
    \label{fig:T0_profiles}
\end{figure}

@@

The most resilient and unexpected feature of MSTE temperature profiles are the pronounced dips adjacent to the boundary layers. 
These dips appear in every solution, regardless of $Ra$. 
Physically, they correspond to thin layers in which the mean temperature gradient reverses, contradicting an important hypothesis of \cite{Malkus_1954}. 
This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
We don't understand the source of these dips, but similar temperature gradient reversals were reported by \cite{chini_cells} along the midlines of 2-dimensional convective cellular solutions at $Ra \sim 10^6$.

\begin{figure*}
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). 
    Advection profiles belong to marginally-stable modes. 
    For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
    For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
    A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
\end{figure*}

Equilibrated states exhibit distinct behaviors for large and small $Ra$. 
This contrast is illustrated in Figure \ref{fig:flux}, where we give heat flux profiles and eigenvalue spectra for two cases: $Ra = 2 \times 10^5$ and $Ra = 10^9$. 
For $Ra = 2 \times 10^5$, there is a single presumed local maximum in the eigenvalue spectrum, whose adjacent modes' advection profiles occupy the bulk of the domain. 
These states have relaxed boundary layers which gradually subside as advection becomes the dominant flux component. 
Such transitional regions do not appear for $Ra = 10^9$, where the shift from diffusion to advection is sharp, requiring pronounced, small-scale advection profiles belonging to modes in the third local maxima pair of the eigenvalue spectrum. 
Traversing towards the midline of the domain, we see increasingly thicker advection profiles corresponding to modes in the second local maxima pair, eventually culminating in the dominant $k_x = 1.5\pi$ mode.

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
    For example, the spectrum corresponding to $Ra = 10^5$ has adjacent marginal wavenumbers $k_x = \pi, \, 1.5\pi$. 
    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three groups of maxima, with a single marginal mode in the first group ($k_x = 1.5\pi$), two adjacent marginal modes in the second group ($k_x = 6\pi, \, 6.5\pi$), and two adjacent marginal modes in the third group ($k_x = 23.5\pi, \, 24\pi$). 
    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\end{figure}

Thermally equilibrated states with large $Ra$ tend to have diverse combinations of marginal modes. 
In every case, the $k_x = 1.5\pi$ mode is included and is often unaccompanied by adjacent modes. 
In Figure \ref{fig:kx_marginals} we give the wavenumbers $k_x$ of marginal modes, color-coded according to their adjacencies. 
Marginal modes often appear in neighboring pairs, where the larger mode is denoted with an x and the smaller mode is denoted with a +. 
In these cases we infer the existence of a local maximum eigenvalue between the two adjacent marginally-stable modes. 
For $Ra \geq 10^6$, a second branch of marginal modes is introduced as shown in light green, obeying some power-law with respect to $Ra$. 
The introduction of this largest branch is likely required to oppose the diffusion of the thinning boundary layers. 
For $Ra \geq 10^8$, a third branch appears (shown in light blue), splitting the widening gap between the other branches. 
This development is associated with moderately thick advection profiles, filling a niche in the total flux by uniting the sharp profiles of the largest branch and those of the bulk-domain-oriented smallest branch.

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumbers (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer heights $\delta$. 
    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
    We expect the minimum $z$ length scale to agree with the boundary layer height $\delta$ because otherwise the boundary layer would continue to diffuse. 
    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layer. 
    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio over various $Ra$.}
    \label{fig:del_inv}
\end{figure}

The largest marginal wavenumber $\max \{ k_x \}$ (represented by the light green branch in Figure \ref{fig:kx_marginals}) serves as a inverse minimum length-scale in the $x$ direction. The finest structures in $\bar{T}(z)$ appear near the boundaries, providing us with a complementary minimum length-scale for $z$. We define the interior boundary layer threshold as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$. In Figure \ref{fig:del_inv}, we illustrate the constant ratio between these two quantities for various $Ra$. The quasilinear model cannot describe small-scale behaviors in either direction. Discretization of the normal modes allows us to collapse the problem into a single dimension, but this comes at a cost.

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer height $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find that $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$, implying $Ra \propto  \delta^{-3}$ which remains consistent with \cite{Malkus_1954}}
    \label{fig:bl_ra}
\end{figure}

In general, MSTE can be characterized by their boundary layer height, from which, the rest of their properties follow. In Figure \ref{fig:bl_ra}, we illustrate the scaling behavior of the boundary layer height $\delta = Ra^{-1/3}$. 
This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable \cite{Malkus_1954}.

\begin{figure*}
    \centering
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for MSTE, aspect-ratio optimized ECS \cite{Wen}, and statistically-steady DNS \cite{Johnston, Scheel_2016}.
    All datasets obey power-law relationships, with the MSTE and ECS admitting classical scaling $\Nu \sim Ra^{1/3}$. 
    MSTE have greater $\Nu$ than the ECS, which in turn, have greater $\Nu$ than the DNS. This can be explained by the contrasting boundary layer geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}
